Recruiting Chapter

### 2020-10-15 manuscript.Rmd
minor changes draft manuscript

Building on these findings, this chapter analyzes off-campus visits to private schools. In particular, we compare visits by public research universities to visits by selective private colleges and universities. The motivation for this public-private comparision is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities. By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities. From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543]. Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.

Analyses are motivated by two, related research questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)? We use social network analysis (SNA) to analyze off-campus recruiting visits. The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407]. An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.

>>>>

Building on these findings, this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities. We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions. Analyses are informed by two broad, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?

The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities. By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities. From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543]. Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.

We use social network analysis (SNA) to analyze off-campus recruiting visits. The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407]. An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.
